Use of management strategy evaluation to inform fisheries management in a changing climate

### 2019-09-10 Poster_ICES.Rmd
fix typo

```{r explicit, fig.cap='Percentage of MSEs that included explicit documentation (colored bars) of SDM process steps --- Roles and meetings --- and adoption of results. In the remaining MSEs was documentation was inexplicit, or absent, and whether the results were adopted was unknown.', fig.height=5.5, out.width="100%"}
text1<-expression(paste("Inexplicit \nor Absent"))
text2<-paste("Absent")
text3<-paste("Unknown")
Freq.plot + annotate("text", x = 8.75, y = 50, label = 'underline("Else")', size=20, parse=TRUE) +
  annotate("text", x = 5, y = 52, label = text1, size=20) + 
  annotate("text", x = 2.6, y = 50, label = text2, size=20) + 
  annotate("text", x = 1, y = 50, label = text3, size=12) +
  theme(text = element_text(size=14))
```

>>>>

```{r explicit, fig.cap='Percentage of MSEs that included explicit documentation (colored bars) of SDM process steps --- Roles and meetings --- and adoption of results. In the remaining MSEs documentation was inexplicit, or absent, and whether the results were adopted was unknown.', fig.height=5.5, out.width="100%"}
text1<-expression(paste("Inexplicit \nor Absent"))
text2<-paste("Absent")
text3<-paste("Unknown")
Freq.plot + annotate("text", x = 8.75, y = 50, label = 'underline("Else")', size=20, parse=TRUE) +
  annotate("text", x = 5, y = 52, label = text1, size=20) + 
  annotate("text", x = 2.6, y = 50, label = text2, size=20) + 
  annotate("text", x = 1, y = 50, label = text3, size=12) +
  theme(text = element_text(size=14))
```
